#Setup
```{r}
setwd("~/ST201R/pro/")
sleepnew<-read.csv("sleepnew.csv", header = TRUE)
head(sleepnew)
```

#full
```{r}
fullnew<-lm(CognitionZscore~., data = sleepnew)
summary(fullnew)
```

```{r}
depressionnew<-lm(CognitionZscore~ DepressionStatus, data = sleepnew)
summary(depressionnew)
#Categorical methods t
```

#One Gender Model
```{r}
sleepgen1<-read.csv("sleepgen1.csv", header = TRUE)
Modelgen1<-lm(CognitionZscore ~ Drinks + ClassYear + DASScore + PoorSleepQuality, data=sleepgen1)
summary(Modelgen1)
#No significant result
```

#Cognition Z Score with one gender
```{r}
sleepgen1<-read.csv("sleepgen1.csv", header = TRUE)
Model2nd<-lm(CognitionZscore ~ LarkOwl + NumEarlyClass + Drinks + AverageSleep + PoorSleepQuality + DepressionScore + DepressionScore*DepressionScore, data=sleep)
summary(Model2nd)
#No significant result

```

#Stepwise one gender
```{r}
null.onegen<-lm(CognitionZscore~1, data = sleepgen1)
full.onegen<-lm(CognitionZscore~., data = sleepgen1)

step(null.onegen, scope = list(lower=null.onegen, upper=full.onegen),direction="forward")
```

#Forward stepwise reccomend: CognitionZscore ~ DASScore + Drinks + Happiness + Lark
#Test result not good, replace happiness and DASScore

#Forward one step test
```{r}
stepres.onegen.forw<-lm(CognitionZscore ~ Drinks + Lark, data = sleepgen1)
summary(stepres.onegen.forw)
```

#Show the autoregression of GPA
```{r}
GPAAuto<-lm(CognitionZscore ~ GPA, data = sleepnew)
summary(GPAAuto)
Anx.Dep<-lm(CognitionZscore ~ AnxietyScore + DepressionScore, data = sleepnew)
summary(Anx.Dep)
vif(Anx.Dep)
```

#New Stepwise
```{r}
null.new<-lm(CognitionZscore~1, data = sleepnew)
full.new<-lm(CognitionZscore~., data = sleepnew)

step(null.new, scope=list(lower=null.new, upper=full.new),direction="forward")
stepres.forward<-lm(formula = CognitionZscore ~ Gender + ClassesMissed + AlcoholUse + StressScore, data = sleepnew)
summary(stepres.forward)
```

#New Stepwise Back
```{r}
step(full.new, data = sleepnew, direction="backward")
stepres.back<-lm(formula = CognitionZscore ~ Gender + NumEarlyClass + EarlyClass + ClassesMissed + DepressionScore + DepressionScoreSq + AlcoholUse, data = sleepnew)
summary(stepres.back)
```

#
```{r}
stepres.back.2<-lm(formula = CognitionZscore ~ Gender  + ClassesMissed + DepressionScore + DepressionScoreSq + AlcoholUse, data = sleepnew)
summary(stepres.back.2)
```

#anova
```{r}
anova(full.new)
```

#3.28 New model from stepwise
```{r}
model.328.2<-lm(CognitionZscore ~ Gender + NumEarlyClass + EarlyClass + ClassesMissed + AlcoholUse + DepressionScore + DepressionScoreSq, data=sleepnew)
summary(model.328.2)
#Some one star, look ok but not good enough
```

#3.28 Interaction term
```{r}
model.328.int1<-lm(CognitionZscore ~ Gender*AlcoholUse + AlcoholUse + Gender + NumEarlyClass + EarlyClass + ClassesMissed +  + StressScore, data=sleepnew)
summary(model.328.int1)
```

#3.28 Plot
```{r}
head(sleepnew) 
summary(sleepnew)
attach(sleepnew)
hist(CognitionZscore)
boxplot(CognitionZscore,horizontal=T,xlab="CognitionZscore")

#3outliers
boxplot(NumEarlyClass,horizontal=T,xlab="NumEarlyClass")
hist(NumEarlyClass)

#3 outliers
hist(PoorSleepQuality)
boxplot(PoorSleepQuality,horizontal=T,xlab="PoorSleepQuality")
summary(PoorSleepQuality)



boxplot(DepressionScore,horizontal=T,xlab="DepressionScore")
summary(DepressionScore)

boxplot(StressScore, horizontal=T,xlab="StressScore")
summary(StressScore)

#6outliers?
boxplot(Happiness,horizontal=T,xlab="Happiness")
#2outliers?
boxplot(AlcoholUse,horizontal=T,xlab="AlcoholUse")
#4 outliers
boxplot(AverageSleep,horizontal=T,xlab="AverageSleep")
summary(AverageSleep)
#4outliers

boxplot(ClassesMissed,horizontal=T,xlab="ClassesMissed")
detach(sleepnew)
```

#why not use classmissed
```{r}
classmissed<-lm(CognitionZscore ~ ClassesMissed, data = sleepnew)
summary(classmissed)
```

#New data input after removing outliers
```{r}
sleep.out<-(read.csv("sleepnoout.csv", header = T))
```

#3.28 New model based on no outliers dataset
```{r}
out.1<-lm(CognitionZscore ~ Gender + EarlyClass + ClassesMissed + EarlyClass*ClassesMissed + DepressionScore + DepressionScoreSq , data=sleep.out)
summary(out.1)
#Interaction term includes EarlyClass*ClassesMissed, as more early class may results in more classes missed
```

# 3.28 Try the above model without removing outlier
```{r}
final.1<-lm(CognitionZscore ~ Gender + EarlyClass*ClassesMissed + DepressionScore + DepressionScoreSq, data=sleepnew)
summary(final.1)
```

# 3.28 Try the above model with AlcoholUse
```{r}
final.2<-lm(CognitionZscore ~ Gender + EarlyClass*ClassesMissed + DepressionScore + DepressionScoreSq + AlcoholUse, data=sleepnew)
summary(final.2)
```

#residual analysis
```{r}
pairs(sleep.out)
```