---
title: "ST201 Project Full Notes"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Setup
##sleepnew is the new dataset with edited value
```{r}
setwd("~/ST201R/pro/")
sleepnew<-read.csv("sleepnew.csv", header = TRUE)
head(sleepnew)
```

#All the important plot
```{r}
head(sleepnew) 
summary(sleepnew)
attach(sleepnew)
hist(CognitionZscore)
boxplot(CognitionZscore,horizontal=T,xlab="CognitionZscore")

#3outliers
boxplot(NumEarlyClass,horizontal=T,xlab="NumEarlyClass")
hist(NumEarlyClass)

#3 outliers
hist(PoorSleepQuality)
boxplot(PoorSleepQuality,horizontal=T,xlab="PoorSleepQuality")
summary(PoorSleepQuality)



boxplot(DepressionScore,horizontal=T,xlab="DepressionScore")
summary(DepressionScore)

boxplot(StressScore, horizontal=T,xlab="StressScore")
summary(StressScore)

#6outliers?
boxplot(Happiness,horizontal=T,xlab="Happiness")
#2outliers?
boxplot(AlcoholUse,horizontal=T,xlab="AlcoholUse")
#4 outliers
boxplot(AverageSleep,horizontal=T,xlab="AverageSleep")
summary(AverageSleep)
#4outliers

boxplot(ClassesMissed,horizontal=T,xlab="ClassesMissed")
detach(sleepnew)
```

#New data input after removing outliers
```{r}
sleep.out<-(read.csv("sleepnoout.csv", header = T))
```
The cook distance test relating to outlier removal is on Xingdian's place, I will ask him to add the code from that part.
##New model based on outlier-removed dataset
```{r}
out.1<-lm(CognitionZscore ~ Gender + EarlyClass + ClassesMissed + EarlyClass*ClassesMissed + DepressionScore + DepressionScoreSq , data=sleep.out)
summary(out.1)
#Interaction term includes EarlyClass*ClassesMissed, as more early class may results in more classes missed
```
Beware that for some reason this is a bit different from the one on the Google Docs. 

#Model with original dataset
```{r}
final.1<-lm(CognitionZscore ~ Gender + EarlyClass*ClassesMissed + DepressionScore + DepressionScoreSq , data=sleepnew)
summary(final.1)
```

# 3.28 Try the above model with AlcoholUse
```{r}
final.2<-lm(CognitionZscore ~ Gender + EarlyClass*ClassesMissed + DepressionScore + DepressionScoreSq + AlcoholUse, data=sleepnew)
summary(final.2)
```

#Cognition - Depression
```{r}
plot(sleepnew$DepressionScore,sleepnew$CognitionZscore, xlab = "Depression Score", ylab = "Cognition Z-Score")

lm1<-lm(sleepnew$CognitionZscore~sleepnew$DepressionScore)
abline(lm1,col="red")
summary(lm1)
summary(sleep$DepressionScore)
```

#Earlyclass - Classmissed
```{r}
plot(sleepnew$EarlyClass,sleepnew$ClassesMissed, xlab = "Easly Class", ylab = "Class missed")

lm3<-lm(sleepnew$ClassesMissed~sleepnew$EarlyClass)
abline(lm3,col="red")
summary(lm3)
summary(sleep$DepressionScore)
```

#residual analysis
```{r}
pairs(sleep.out)
```
```{r}
pairs(sleepnew)
```

#anova
```{r}
anova(final.1)
```

#anova 2
```{r}
anova(final.2)
```

#Leverage - Hat values

#Influencence

Rearrange word document
Methodology of lay report
Policy suggestion
Graph of lay report

```{r}
sleepdep<-lm(AnxietyScore ~ Owl + Lark + PoorSleepQuality + AverageSleep + AlcoholUse, data = sleepnew)
summary(sleepdep)
```

```{r}
plot(sleepnew$PoorSleepQuality,sleepnew$DepressionScore, xlab = "Sleep Quality Marks", ylab = "Depression Score")
lmd<-lm(sleepnew$DepressionScore~sleepnew$PoorSleepQuality)
abline(lmd,col="red")


plot(sleepnew$PoorSleepQuality,sleepnew$AnxietyScore, xlab = "Sleep Quality Marks", ylab = "Anxiety Score")
lma<-lm(sleepnew$AnxietyScore~sleepnew$PoorSleepQuality)
abline(lma,col="red")


plot(sleepnew$PoorSleepQuality,sleepnew$StressScore, xlab = "Sleep Quality Marks", ylab = "Stress Score")
lms<-lm(sleepnew$StressScore~sleepnew$PoorSleepQuality)
abline(lms,col="red")

```

```{r}
Sleep<-read.table("sleepnew.txt",header=T)
attach(Sleep)
lm1<-lm(GPA~Gender,data=Sleep)
#Final Model
#Zscore = Gender + EarlyClass + ClassesMissed + EarlyClass*ClassesMissed + Depression + Depression^2
DepressionSq=Sleep$DepressionScore^2
lmfinal<-lm(CognitionZscore~Gender+EarlyClass+ClassesMissed+EarlyClass*ClassesMissed+DepressionSq+DepressionScore, data=Sleep)
anova(lmfinal)

#Outliers of our final model
lmfinal.stdres = rstandard(lmfinal)
summary(lmfinal.stdres)
help(rstandard)
show(lmfinal.stdres)
outliers = c(lmfinal.stdres>3)
show(outliers)

#outliers of ALL individual models (assuming only 1 x variable)
lm1<-lm(CognitionZscore~GPA,data=Sleep)
lm1.stdres = rstandard(lm1)
show(lm1.stdres>3)

lm2<-lm(CognitionZscore~NumEarlyClass,data=Sleep)
lm2.stdres = rstandard(lm2)
show(lm2.stdres>3)

lm3<-lm(CognitionZscore~ClassesMissed,data=Sleep)
lm3.stdres = rstandard(lm3)
show(lm3.stdres>3)

lm4<-lm(CognitionZscore~DepressionScore,data=Sleep)
lm4.stdres = rstandard(lm4)
show(lm4.stdres>3)

lm5<-lm(CognitionZscore~StressScore,data=Sleep)
lm5.stdres = rstandard(lm5)
show(lm5.stdres>3)

lm6<-lm(CognitionZscore~AnxietyScore,data=Sleep)
lm6.stdres = rstandard(lm6)
show(lm6.stdres>3)

lm7<-lm(CognitionZscore~DASScore,data=Sleep)
lm7.stdres = rstandard(lm7)
show(lm7.stdres>3)

lm8<-lm(CognitionZscore~AlcoholUse,data=Sleep)
lm8.stdres = rstandard(lm8)
show(lm8.stdres>3)

lm9<-lm(CognitionZscore~AverageSleep,data=Sleep)
lm9.stdres = rstandard(lm9)
show(lm9.stdres>3)


#Leverage, by using hat values
#In this case, p=number of indepent variables=28
lmfinal.hat= hatvalues(final.1)
show(lmfinal.hat>0.2292)
#Point 25 172! are highly likely to have high leverage



#Influence, by using cook's distance
plot(final.1, which = c(4))
#point 25 172 and 182 should be removed



```